---
title: "martah_OriginalHomeworkCode_02"
author: "Marta" 
date: "9/23/2021"
output: html_document
---      

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Alright I'm starting with an attempt to use poissson distribution. _Sorry in advance Zoe :,)_

###ZOE: I really like that you got rid of all of the messy-ness up front.  I wonder if we will ever need to have any of it, or if it is always just excess?

``` {r poisson}
x<- rpois(1, 15) #where 1 is the n value since its 15 is the  mean of the two hours and 15 is the mean or lambda
x

###ZOE: Thank you for teaching me how to add a title to the r section of each chunk!
```
``` {r lessthan}
ppois(8, (rpois(1, 15)), lower=FALSE) #I can't tell if I should be running lambda as 15 for the mean or x  where x is therpois? or as i put here, lmbda being the function of rpois?

###ZOE:I think that maybe you should use dpois for x (8) and l(15), and the inverse of ppois at the end (1-ppois)  
```
``` {r nocalls}
dpois(0, 15) #same problem but this time i set lambda as 15

###ZOE: This is exactly how I would do this one. 
```
``` {r 3calls}
dpois(3, 15)
```
All these probabilities are incredibly low which is why I don't trust I'm using the right function.

###ZOE:I still think they are right, although I am having a hard time visualizing what the statistics really mean.  But, it should always be a number under one if I am not mistaken.  

``` {r 1-30}
calls<- 0:30
plot(calls, dpois(calls, 15))

###ZOE:I think that you should more specifically call it a bar plot. (barplot(dpois(x,l)))
```
``` {r 104}
exampledist<- rpois(104, 15)
exampledist

###ZOE:Exampledist is the same thing as assigning to a variable letter but more clear.  That is really helpful to see. 
```
``` {r hist}
hist(exampledist, freq = FALSE, col = "blue", main = "Titi Calls Over 2 Years", xlab = "unknown",
    ylab = "uk", xlim = c(0, 30))

###ZOE: We worked though this one together.  Learned how to do colors. Breaks spaces out the individual bars. 
```
I am so confused on the y-axis, this is coming up as more of a barplot than I wanted??? I want to see the individual points for each weekend but I have no clue what is missing? I'm still struggling with packages so I think ggplot and manipulate are what I need but I'm not sure how.

## Challenges

1. I'm very concerned with how low my probabilities are in the first section, part of the problem is I'm not sure of the magnitude of the values like should they be over 1, under 1, etc.? 
  ###ZOE: Because its a probability, it should be under one?
2. With lambda, if I use `x` that is a variable variable if that makes sense. It vastly changes the results if I use x, 15 (the mean), or the function itself. I simply do not know what is the proper lambda is??
  ###ZOE:I also struggled with this.  I think 15 has more significance than just her hypothesis. 
3. This is a content question, I am not sure when I should be assigning functions to an element. The examples will usually use the function every time but I'm not sure.    
4. The syntax for `rpois` was really confusing a first and now I'm worried it seems to easy. I am operating on (number of vectors, mean) essentially.
###ZOE:No overthinking!  You got this.  It is simple once we figured it out.     
5. In the final histogram I mention this but I want this plotted with a point for every weekend, not a barplot of overall means. I'm not sure a) how to do this and b) if I'm even suppose to be doing this
###ZOE:I think we discussed/decided that this should be frequency of calls per hour.